Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-21 talk_ucl_cdt_200622/introduction.tex
remove dot from methodology slide
Data generation slide updated.

\begin{frame}
	\frametitle{Project Background}
	Nuclear fusion -- the energy of the future!
    \vspace{10pt}
	\begin{itemize}
	    \item Must produce and contain an extremely hot and dense plasma
	    \begin{itemize}
		    \item Magnetic Confinement Fusion (MCF): toroidal circulation
		    \item Inertial Confinement Fusion (ICF): spherical compression
		\end{itemize}
		\vspace{10pt}
		\item Modern designs require enriched Hydrogen fuel of two varieties:
	    \begin{itemize}
		    \item Deuterium ($^2$H) -- abundant in naturally-sourced water
		    \item Tritium ($^3$H) -- extremely rare, but can be produced \textit{in-reactor}
		\end{itemize}
	\end{itemize}
	\vspace{10pt}
	\centering{\includegraphics[height=3cm]{icf_diagram}}
\end{frame}

@@

\begin{frame}
	\frametitle{Data Generation}
	We designed the Approximate TBR Evaluator (ATE) package to generate training and test datasets from Paramak.\newline
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-7cm-5mm}

        Deployed Paramak on UCL's Hypatia cluster:
        \begin{itemize}
            \item Generated 1M samples
            \item 27 days of runtime
        \end{itemize}

@@

        Two classes of runs:
        \begin{itemize}
            \item Full -- 18 discrete and continuous parameters
            \item Slice -- 11 continuous parameters
        \end{itemize}

>>>>

\begin{frame}
	\frametitle{Project Background}
	Nuclear fusion -- the energy of the future!
    \vspace{10pt}
	\begin{itemize}
	    \item Must produce and contain an extremely hot and dense plasma
	    \begin{itemize}
		    \item Magnetic Confinement Fusion (MCF): toroidal circulation
		    \item Inertial Confinement Fusion (ICF): spherical compression
		\end{itemize}
		\vspace{10pt}
		\item Modern designs require enriched Hydrogen fuel of two varieties:
	    \begin{itemize}
		    \item Deuterium ($^2$H) -- abundant in naturally-sourced water.
		    \item Tritium ($^3$H) -- extremely rare, but can be produced \textit{in-reactor}.
		\end{itemize}
	\end{itemize}
	\vspace{10pt}
	\centering{\includegraphics[height=3cm]{icf_diagram}}
\end{frame}

@@

\begin{frame}
	\frametitle{Data Generation}
	We produced training and test datasets by uniform random sampling over the 7 discrete and 11 continuous parameters of Paramak.\newline
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-7cm-5mm}

        Paramak was deployed on UCL's Hypatia cluster:
        \begin{itemize}
            \item Generated 1M samples.
            \item 27 days of runtime.
        \end{itemize}

@@

        Two classes of runs:
        \begin{itemize}
            \item All parameters free.
            \item Discrete fixed, continuous free.
        \end{itemize}
